Fundamental Problems with the Evidence Base of Adolescent Depression Treatments.

### 2024-03-14 apples_and_oranges.qmd
More tabulating, running t tests for control vs active comparison in psy trials

# Start by looking at demographics at baseline
# Currently we have both control and active conditions, we just need each study once

@@

# Now start looking at perc_women variable

# The metagen function doesn't like when NAs result in the TE vector being a different length to subgroup vector. Need to start by removing NAs.

@@

# Apply the function to the meta-analysis result
results_met_perc_women_overall <- extract_stats(met_perc_women_overall)

knitr:: kable(results_met_perc_women_overall, caption = "Gender composition")

@@

knitr:: kable(results_met_perc_women_clin, caption = "Gender composition in clinical studies")

@@

#  grab ids for those studies
cbt_meds_study_ids <-
  df_appl_v_orange[df_appl_v_orange$active_type == "cbt" | df_appl_v_orange$active_type == "Fluoxetine" | df_appl_v_orange$active_type == "Escitalopram",]$new_study_id

# Use those ids to subset all dataframes in the list

@@

knitr:: kable(results_met_perc_women_cbt, caption = "Gender composition in studies with CBT, escitalopram or fluoxetine")

@@

knitr:: kable(results_met_perc_women_no_wl, caption = "Gender composition in studies with CBT, escitalopram or fluoxetine")

@@

Psychotherapy trials featured a significantly higher percentage of women when compared to medication trials (`results_met_perc_women_overall$pval_between`). On average, samples were comprised of `r results_met_perc_women_overall$TE_random[results_met_perc_women_overall$subgroup == 1]`% (*SE* = `r results_met_perc_women_overall$seTE_random[results_met_perc_women_overall$subgroup == 1]` women across psychotherapy trials and `r results_met_perc_women_overall$TE_random[results_met_perc_women_overall$subgroup == 0]`% (*SE* = `r results_met_perc_women_overall$seTE_random[results_met_perc_women_overall$subgroup == 0]`women across medication trials.  Excluding sub-clinical studies yielded very similar results (p = `results_met_perc_women_clin$pval_between`). This difference in gender composition however did not reach statistical significance when only CBT, fluoxetine and escitalopram trials were included (p = `results_met_perc_women_cbt$pval_between`).

@@

knitr:: kable(results_met_age, caption = "Average age in psychotherapy vs medication trials")

@@

knitr:: kable(results_met_age_clin, caption = "Average age in clinical studies")

@@

knitr:: kable(results_met_age_cbt, caption = "Average age in cbt, fluox, escit studies")

@@

### Age

```{r, warning=FALSE, message = FALSE, echo=FALSE}
# Now look at baseline severity for overall psy vs med
# Need to calculate the variables first

knitr:: kable(results_met_sev, caption = "Baseline Depression Severity in Psychotherapy vs Medication trials")

knitr:: kable(results_met_sev_clin, caption = "Baseline Depression Severity in Psychotherapy vs Medication trials, excluding subclinical studies")

df_for_baseline_severity_cbt <- df_for_baseline_severity %>%
  filter(new_study_id %in% cbt_meds_study_ids) %>%

knitr:: kable(results_met_sev_cbt, caption = "Baseline Depression Severity in Psychotherapy vs Medication trials with CBT, fluoxetine and escitaloptram as the active intervention")

# plot for overall severity results

ggplot(df_for_baseline_severity, aes(x = factor(psy_or_med), y = perc_baseline_mean, color = factor(psy_or_med))) +
  geom_point(position = position_jitter(width = 0.2), size = 2) +
  labs(
    title = "Baseline Depression Severity in Psychotherapy vs Medication trials",
    x = "Treatment Modality",
    y = "Baseline Depression Levels (transformed)",
    color = "Treatment Type"
  ) +
  scale_color_discrete(labels = c("Medication", "Psychotherapy"))

# Now overall
# Lets make a table that combines across these baseline characteristics variables

# Rounding
df_overall_baseline_results <- df_overall_baseline_results %>%
  mutate(across(where(is.numeric), ~round(., 2)))

df_overall_baseline_results %>%
  kbl(caption = "Table X: Sample characteristics at baseline across medication and psychotherapy studies") %>%
  kable_material(bootstrap_options = c("hover", "condensed", "bordered"), full_width = FALSE) %>%
  row_spec(row = 0, background = "#EBEBEB", extra_css = "border-bottom: 1px black;" ) %>% 
  row_spec(row = 1, bold = T) %>% 
  row_spec(c(4, 7), bold = T, extra_css = "border-top: 1px solid black;") %>%
  column_spec(column = 1, border_right = T) %>% 
  add_indent(c(2, 3, 5, 6, 8, 9)) %>% 
  footnote(alphabet = c("Values for baseline severity represent the percentage transformed depression scores", "pval_between = the p-value from the test for subgroup differences from the relevant meta-analysis"))

On average, severity of depressive symptoms at baseline was significantly higher in medication trials when compared to psychotherapy trials, for both the overall sample (p = `results_met_sev$pval_between`) and when taking only those studies where the active arm was either CBT, fluoxetine or escitalopram (p = `results_met_sev_cbt$pval_between`). When excluding psychotherapy studies that recruited samples with sub-clinical depression, this difference did not reach statistical significance (p = `results_met_sev_clin$pval_between`).

@@

# ### do ALL studies using percentage at baseline
# all_studies_baseline_metareg <- list_df_simulated_percentage[[1]]
# 
# #turn sds to sec
# all_studies_baseline_metareg$baseline_stand_error <- all_studies_baseline_metareg$perc_baseline_sd/
#                                         sqrt(all_studies_baseline_metareg$baseline_n)
# 
# model_1 <- as.formula(~ four_level_var)
# condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
#                                                               #throughout
# # also change this for the function to work
# all_studies_baseline_metareg$baseline_mean <- all_studies_baseline_metareg$perc_baseline_mean
# results_all_studies_metareg_baseline <- run_metareg_and_extract(all_studies_baseline_metareg,  
#                                                          model_1, condition)
# 
# ### get CDRS studies
# cdrs_studies_for_baseline_metareg <- list_cdrs_study[[1]] # created this above, you can take any of these, as the means and sds are repeated.
# 
# #turn sds to sec
# cdrs_studies_for_baseline_metareg$baseline_stand_error <- cdrs_studies_for_baseline_metareg$baseline_sd/
#                                         sqrt(cdrs_studies_for_baseline_metareg$baseline_n)
# 
# model_1 <- as.formula(~ four_level_var)
# condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
#                                                               #throughout
# 
# results_cdrs_metareg_baseline <- run_metareg_and_extract(cdrs_studies_for_baseline_metareg,  
#                                                          model_1, condition)
# 
# ### get HAM-D studies
# hamd_study_ids <-
#   df_appl_v_orange[df_appl_v_orange$instrument_name == "hamd",]$new_study_id
# 
# list_hamd_study <- list_df_simulated[[1]][list_df_simulated[[1]]$new_study_id
#                                                           %in% hamd_study_ids,]
# 
# hamd_studies_for_baseline_metareg <- list_hamd_study # 
# 
# #turn sds to sec
# hamd_studies_for_baseline_metareg$baseline_stand_error <- hamd_studies_for_baseline_metareg$baseline_sd/
#                                         sqrt(hamd_studies_for_baseline_metareg$baseline_n)
# 
# model_1 <- as.formula(~ four_level_var)
# condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
#                                                               #throughout
# results_hamd_metareg_baseline <- run_metareg_and_extract(hamd_studies_for_baseline_metareg, 
#                                                          model_1, condition)
# 
# results_hamd_metareg_baseline$condition <-  levels(list_df_simulated[[1]]$four_level_var)

### Number of trial sites

@@

### Comparing the nature and intensity of control conditions in psychotherapy trials

@@

group_function <- function(dataframe, my_groups, columns) {
  result_dataframe <- data.frame(
    Group = character(),
    Column = character(),
    N = numeric(),
    Mean = numeric(),
    Std_Dev = numeric(),
    Median = numeric(),
    IQR = numeric(),
    stringsAsFactors = FALSE
  )
  unique_groups <- unique(dataframe[[my_groups]])
  for (group in unique_groups) {
    group_data <- dataframe[dataframe[[my_groups]] == group, ]
    for (col in columns) {
      col_data <- group_data[[col]]
      n <- sum(!is.na(col_data))
      mean_val <- mean(col_data, na.rm = TRUE)
      std_dev <- sd(col_data, na.rm = TRUE)
      median_val <- median(col_data, na.rm = TRUE)
      iqr <- IQR(col_data, na.rm = TRUE)
      result_dataframe <- rbind(result_dataframe,
                                data.frame(Group = group,
                                           Column = col, N = n, Mean = mean_val,
                                           Std_Dev = std_dev, Median = median_val,
                                           IQR = iqr, stringsAsFactors = FALSE))
    }
  }
  return(result_dataframe)
}

@@

knitr:: kable(control_summary, caption="Characteristics of the active and control arms of psychotherapy trials")

@@

# Gender first

# Now overall
# Lets make a table that combines across these baseline characteristics variables

# Rounding
df_overall_baseline_results <- df_overall_baseline_results %>%
  mutate(across(where(is.numeric), ~round(., 2)))

df_overall_baseline_results %>%
  kbl(caption = "Table X: Sample characteristics at baseline across medication and psychotherapy studies") %>%
  kable_material(bootstrap_options = c("hover", "condensed", "bordered"), full_width = FALSE) %>%
  row_spec(row = 0, background = "#EBEBEB", extra_css = "border-bottom: 1px black;" ) %>% 
  row_spec(row = 1, bold = T) %>% 
  row_spec(c(4, 7), bold = T, extra_css = "border-top: 1px solid black;") %>%
  column_spec(column = 1, border_right = T) %>% 
  add_indent(c(2, 3, 5, 6, 8, 9)) %>% 
  footnote(alphabet = c("Values for baseline severity represent the percentage transformed depression scores", "pval_between = the p-value from the test for subgroup differences from the relevant meta-analysis"))

>>>>

```{r, warning=FALSE, message = FALSE, echo=FALSE}
# Start by looking at demographics at baseline
# Currently we have both control and active conditions, we just need each study once

@@

# Now look at baseline severity for overall psy vs med
# Need to calculate the variables first

cbt_meds_study_ids <-
  df_appl_v_orange[df_appl_v_orange$active_type == "cbt" | df_appl_v_orange$active_type == "Fluoxetine" | df_appl_v_orange$active_type == "Escitalopram",]$new_study_id

df_for_baseline_severity_cbt <- df_for_baseline_severity %>%
  filter(new_study_id %in% cbt_meds_study_ids)

# no wl

df_for_baseline_severity_no_wl <- df_for_baseline_severity %>%
  filter(new_study_id %in% no_wl_ids)

met_sev_no_wl <- metagen(TE = perc_baseline_overall,
                           seTE = perc_se_baseline,
                           studlab = new_study_id,
                           data = df_for_baseline_severity_no_wl,
                           sm = "",
                           fixed = FALSE,
                           random = TRUE,
                           method.tau = "REML",
                           hakn = TRUE,
                           title = "baseline severity no wl studies",
                           subgroup = psy_or_med,
                           tau.common = FALSE)

results_met_sev_no_wl <- extract_stats(met_sev_no_wl)

On average, severity of depressive symptoms at baseline was significantly higher in medication trials when compared to psychotherapy trials for the overall sample (p = `results_met_sev$pval_between`).The statistics provided in Table 1 represent the transformed mean scores at baseline on the

and when taking only those studies where the active arm was either CBT, fluoxetine or escitalopram (p = `results_met_sev_cbt$pval_between`). When excluding psychotherapy studies that recruited samples with sub-clinical depression, this difference did not reach statistical significance (p = `results_met_sev_clin$pval_between`).

# Now start looking at perc_women variable 
# The metagen function doesn't like when NAs result in the TE vector being a different length to subgroup vector. Need to start by removing NAs.

@@

# Apply the function to the meta-analysis result

results_met_perc_women_overall <- extract_stats(met_perc_women_overall)

@@

@@

@@

@@

@@

Psychotherapy trials featured a significantly higher percentage of women when compared to medication trials (`results_met_perc_women_overall$pval_between`). On average, samples were comprised of `r results_met_perc_women_overall$TE_random[results_met_perc_women_overall$subgroup == 1]`% (*SE* = `r results_met_perc_women_overall$seTE_random[results_met_perc_women_overall$subgroup == 1]` women across psychotherapy trials and `r results_met_perc_women_overall$TE_random[results_met_perc_women_overall$subgroup == 0]`% (*SE* = `r results_met_perc_women_overall$seTE_random[results_met_perc_women_overall$subgroup == 0]`women across medication trials. Excluding sub-clinical studies (p = `results_met_perc_women_clin$pval_between`) and studies that used waitlist as their control condition yielded very similar results (p = `results_met_perc_women_no_wl$pval_between`). This difference in gender composition however did not reach statistical significance when only CBT, fluoxetine and escitalopram trials were included (p = `results_met_perc_women_cbt$pval_between`).

@@

@@

@@

# Now excluding wl

df_for_age_metan_no_wl <- df_for_age_metan %>%
  filter(new_study_id %in% no_wl_ids)

met_age_no_wl <- metagen(TE = mean_age,
                           seTE = se_age,
                           studlab = new_study_id,
                           data = df_for_age_metan_no_wl,
                           sm = "",
                           fixed = FALSE,
                           random = TRUE,
                           method.tau = "REML",
                           hakn = TRUE,
                           title = "age across no wl studies",
                           subgroup = psy_or_med,
                           tau.common = FALSE)

results_met_age_no_wl <- extract_stats(met_age_no_wl)

```
### Age

# Lets make a table that combines across these baseline characteristics variables

# Define new column names
new_column_names <- c("Subgroup", "K", "Mean", "SE", "Lower CI", "Upper CI", "T2", "p-value")

# Assign new column names to the data frame
colnames(df_overall_baseline_results) <- new_column_names

# Rounding
df_overall_baseline_results <- df_overall_baseline_results %>%
  mutate(across(.cols = 2:(ncol(.) - 1), ~ round(., 2))) %>%
  mutate_at(vars(ncol(.)), ~ round(., 3))

colnames(df_overall_baseline_results)[8] <- paste0(colnames(df_overall_baseline_results)[8], footnote_marker_number(1))

df_overall_baseline_results %>%
  kbl(align = "l", caption = "Table X: Sample characteristics at baseline across medication and psychotherapy studies", escape = F) %>%
  kable_material(bootstrap_options = c("hover", "condensed", "bordered"), full_width = FALSE) %>%
  row_spec(row = 0, background = "#EBEBEB", extra_css = "border-bottom: 1px black;" ) %>% 
  row_spec(row = 1, bold = T) %>% 
  row_spec(c(4, 7), bold = T, extra_css = "border-top: 1px solid black;") %>%
  column_spec(1, border_right = T) %>% 
  add_indent(c(2, 3, 5, 6, 8, 9)) %>% 
  footnote(number = c("Statistic derived from the test for subgroup differences in the relevant meta-analysis"))

@@

@@

sites_t_test_stats <- data.frame(
  statistic = sites_t_test$statistic,
  df = sites_t_test$parameter,
  p_value = sites_t_test$p.value,
  ci_lower = sites_t_test$conf.int[1],
  ci_upper = sites_t_test$conf.int[2]
)

sites_t_test_stats <- sites_t_test_stats %>%
  dplyr:: mutate(across(.cols = c(statistic, df, ci_lower, ci_upper), ~ round(., 2)))

sites_t_test_stats %>%
  kbl(caption = "Table X: Results for t-test comparing number of sites between medication and psychotherapy studies") %>% 
  kable_material(bootstrap_options = c("hover", "condensed", "bordered"), full_width = FALSE) %>% 
  row_spec(row = 0, background = "#EBEBEB") %>% 
  column_spec(column = 1, border_right = T)

```
### Number of trial sites

@@

@@

group_function <- function(dataframe, my_groups, columns) {
  result_dataframe <- data.frame(
    Group = character(),
    Column = character(),
    N = numeric(),
    Mean = numeric(),
    SD = numeric(),
    Median = numeric(),
    IQR = numeric(),
    stringsAsFactors = FALSE
  )
  unique_groups <- unique(dataframe[[my_groups]])
  for (group in unique_groups) {
    group_data <- dataframe[dataframe[[my_groups]] == group, ]
    for (col in columns) {
      col_data <- group_data[[col]]
      n <- sum(!is.na(col_data))
      mean_val <- mean(col_data, na.rm = TRUE)
      SD <- sd(col_data, na.rm = TRUE)
      median_val <- median(col_data, na.rm = TRUE)
      iqr <- IQR(col_data, na.rm = TRUE)
      result_dataframe <- rbind(result_dataframe,
                                data.frame(Group = group,
                                           Column = col, N = n, Mean = mean_val,
                                           SD = SD, Median = median_val,
                                           IQR = iqr, stringsAsFactors = FALSE))
    }
  }
  return(result_dataframe)
}

@@

control_summary <- control_summary %>% 
  select(-c(Column, Median, IQR))

control_summary <- control_summary %>%
  mutate(Group = case_when(
    Group == "psychotherapy_active" ~ "Active",
    Group == "psychotherapy_control" ~ "Control",
    TRUE ~ as.character(Group)  # Keep other values unchanged
  ))

control_summary <- control_summary %>% 
  mutate(across(where(is.numeric), ~round(., 2)))

control_summary %>%
  kbl(align = "l", caption = "Table X: Comparing the intensity of the intervention between active and control arms of psychotherapy studies", escape = F) %>%
  kable_material(bootstrap_options = c("hover", "condensed", "bordered"), full_width = FALSE) %>%
  row_spec(row = 0, background = "#EBEBEB", extra_css = "border-bottom: 1px black;" ) %>% 
  column_spec(1, border_right = T) %>% 
  pack_rows("Number of sessions", 1, 2) %>% 
  pack_rows("Frequency (weeks)", 3, 4) %>% 
  pack_rows("Session length (mins)", 5, 6) %>%
  pack_rows("Total intervention hours", 7, 8) %>%
  pack_rows("Total intervention period (weeks)", 9, 10)

# t tests

session_no_t_test <- t.test(no_sessions ~ levels_var, data = df_descr_psy_conditions)
freq_t_test <- t.test(freq_weeks ~ levels_var, data = df_descr_psy_conditions)
session_length_t_test <- t.test(length_sessions_mins ~ levels_var, data = df_descr_psy_conditions)
total_hours_t_test <- t.test(total_hours ~ levels_var, data = df_descr_psy_conditions)
total_period_t_test <- t.test(total_period_weeks ~ levels_var, data = df_descr_psy_conditions)

extract_t_test_stats <- function(df) {

  t_test_stats <- data.frame(
  outcome = df$data.name,
  statistic = df$statistic,
  df = df$parameter,
  p_value = df$p.value,
  ci_lower = df$conf.int[1],
  ci_upper = df$conf.int[2])

  return(t_test_stats)

results_session_no_t_test <- extract_t_test_stats(session_no_t_test)
results_freq_t_test <- extract_t_test_stats(freq_t_test)
results_session_length_t_test <- extract_t_test_stats(session_length_t_test)
results_total_hours_t_test <- extract_t_test_stats(total_hours_t_test)
results_total_period_t_test <- extract_t_test_stats(total_period_t_test)

control_summary_t_tests <- rbind(results_session_no_t_test, results_freq_t_test, results_session_length_t_test, results_total_hours_t_test, results_total_period_t_test)

```
### Comparing the nature and intensity of control conditions in psychotherapy trials

@@

# Lets make a table that combines across the sensitivity analyses for severity

df_severity_sens <- rbind(results_met_sev_cbt, results_met_sev_clin, results_met_sev_no_wl)

# For row names
df_severity_sens <- df_severity_sens %>%
  mutate(subgroup = case_when(
    row_number() == 1 ~ "CBT, fluoxetine and escitalopram",
    row_number() == 4 ~ "Excluding subclinical",
    row_number() == 7 ~ "Excluding waitlist",
    TRUE ~ if_else(subgroup == 0, "Medication", "Psychotherapy")
  ))

# Define new column names
new_column_names <- c(" ", "K", "Mean", "SE", "Lower CI", "Upper CI", "T2", "p-value")

# Assign new column names to the data frame
colnames(df_severity_sens) <- new_column_names

# Rounding
df_severity_sens <- df_severity_sens %>%
  mutate(across(.cols = 2:(ncol(.) - 1), ~ round(., 2))) %>%
  mutate_at(vars(ncol(.)), ~ round(., 3))

colnames(df_severity_sens)[8] <- paste0(colnames(df_severity_sens)[8], footnote_marker_number(1))

df_severity_sens %>%
  kbl(align = "l", caption = "Table X: Sensitivity analyses for comparison of baseline severity levels between psychotherapy and medication trials", escape = F) %>%
  kable_material(bootstrap_options = c("hover", "condensed", "bordered"), full_width = FALSE) %>%
  row_spec(row = 0, background = "#EBEBEB", extra_css = "border-bottom: 1px black;" ) %>% 
  row_spec(row = 1, bold = T) %>% 
  row_spec(c(4, 7), bold = T, extra_css = "border-top: 1px solid black;") %>%
  column_spec(1, border_right = T) %>% 
  add_indent(c(2, 3, 5, 6, 8, 9)) %>% 
  footnote(number = c("Statistic derived from the test for subgroup differences in the relevant meta-analysis"))

# Now gender

df_gender_sens <- rbind(results_met_perc_women_cbt, results_met_perc_women_clin, results_met_perc_women_no_wl)

# For row names
df_gender_sens <- df_gender_sens %>%
  mutate(subgroup = case_when(
    row_number() == 1 ~ "CBT, fluoxetine and escitalopram",
    row_number() == 4 ~ "Excluding subclinical",
    row_number() == 7 ~ "Excluding waitlist",
    TRUE ~ if_else(subgroup == 0, "Medication", "Psychotherapy")
  ))

# Define new column names
new_column_names <- c(" ", "K", "Mean", "SE", "Lower CI", "Upper CI", "T2", "p-value")

# Assign new column names to the data frame
colnames(df_gender_sens) <- new_column_names

# Rounding
df_gender_sens <- df_gender_sens %>%
  mutate(across(.cols = 2:(ncol(.) - 1), ~ round(., 2))) %>%
  mutate_at(vars(ncol(.)), ~ round(., 3))

colnames(df_gender_sens)[8] <- paste0(colnames(df_gender_sens)[8], footnote_marker_number(1))

df_gender_sens %>%
  kbl(align = "l", caption = "Table X: Sensitivity analyses for comparison of gender composition between psychotherapy and medication trials", escape = F) %>%
  kable_material(bootstrap_options = c("hover", "condensed", "bordered"), full_width = FALSE) %>%
  row_spec(row = 0, background = "#EBEBEB", extra_css = "border-bottom: 1px black;" ) %>% 
  row_spec(row = 1, bold = T) %>% 
  row_spec(c(4, 7), bold = T, extra_css = "border-top: 1px solid black;") %>%
  column_spec(1, border_right = T) %>% 
  add_indent(c(2, 3, 5, 6, 8, 9)) %>% 
  footnote(number = c("Statistic derived from the test for subgroup differences in the relevant meta-analysis"))

# Now age

df_age_sens <- rbind(results_met_age_cbt, results_met_age_clin, results_met_age_clin)

# For row names
df_age_sens <- df_age_sens %>%
  mutate(subgroup = case_when(
    row_number() == 1 ~ "CBT, fluoxetine and escitalopram",
    row_number() == 4 ~ "Excluding subclinical",
    row_number() == 7 ~ "Excluding waitlist",
    TRUE ~ if_else(subgroup == 0, "Medication", "Psychotherapy")
  ))

# Define new column names
new_column_names <- c(" ", "K", "Mean", "SE", "Lower CI", "Upper CI", "T2", "p-value")

# Assign new column names to the data frame
colnames(df_age_sens) <- new_column_names

# Rounding
df_age_sens <- df_age_sens %>%
  mutate(across(.cols = 2:(ncol(.) - 1), ~ round(., 2))) %>%
  mutate_at(vars(ncol(.)), ~ round(., 3))

colnames(df_age_sens)[8] <- paste0(colnames(df_age_sens)[8], footnote_marker_number(1))

df_age_sens %>%
  kbl(align = "l", caption = "Table X: Sensitivity analyses for comparison of age between psychotherapy and medication trials", escape = F) %>%
  kable_material(bootstrap_options = c("hover", "condensed", "bordered"), full_width = FALSE) %>%
  row_spec(row = 0, background = "#EBEBEB", extra_css = "border-bottom: 1px black;" ) %>% 
  row_spec(row = 1, bold = T) %>% 
  row_spec(c(4, 7), bold = T, extra_css = "border-top: 1px solid black;") %>%
  column_spec(1, border_right = T) %>% 
  add_indent(c(2, 3, 5, 6, 8, 9)) %>% 
  footnote(number = c("Statistic derived from the test for subgroup differences in the relevant meta-analysis"))
